Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-19 papers/EMNLP2019/modeling.tex
--

The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}, and the references therein).

>>>>

The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).
